The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-07 talk/vmil2012/paper.tex
chapter -> paper

The papers does not describe any attempts to share the object entries and scope
entries between different deoptimization safe points. This seems to not be
needed in a method-based JIT compiler, because method-based JITs have fewer
deoptimization points than tracing JITs. Indeed, in the evaluation presented in
the second paper~\cite{kotzmann_run-time_2007} the number of safe points is low
for the benchmarks presented there, between 167 and 1512.\footnote{The fact
that the density of safe points is low also means that the sharing approaches
of this chapter likely would not work well.} The size of the
debugging information in the presented benchmarks is at most about half the
size of the machine code generated.

>>>>

The papers does not describe any attempts to share the object entries and scope
entries between different deoptimization safe points. This seems to not be
needed in a method-based JIT compiler, because method-based JITs have fewer
deoptimization points than tracing JITs. Indeed, in the evaluation presented in
the second paper~\cite{kotzmann_run-time_2007} the number of safe points is low
for the benchmarks presented there, between 167 and 1512.\footnote{The fact
that the density of safe points is low also means that the sharing approaches
of this paper likely would not work well.} The size of the
debugging information in the presented benchmarks is at most about half the
size of the machine code generated.
